BurgerTown Presents: Open Adcess

### 2017-04-08 aesthetics.tex
added some files

ACM pep rallies: a single academic article will be fired from a cannon but invariably so many people fight over it it just shreds to pieces

@@

>>>>

ACM pep rallies: a single academic article will be fired from a t-shirt cannon but invariably so many people fight over it it just shreds to pieces

@@

jewel heists for the ACM, decadent society gadabout for the ACM

ACM rigged casino PL

We can't have papers floating around everywhere. A researcher is liable to make a pass at the Truth.
